\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Learning goals}
\author{Joop}
\date{June 2014}

\begin{document}

\maketitle

\section*{Joop's Learning Goals}
When starting the project we all put some goals for ourselves to be reached at the end of the project. 
My learning goals were as follows
\begin{itemize}
	\item Improve testing abilities
	\item Acquire project manager experience and skills
	\item Have a clearer view of how projects are done.
\end{itemize}

I am happy to say that I am satisfied with what I have achieved and learned during the project. When I started with the project I wanted to be the project manager, since this role interests me and I wanted to figure out whether this is a role I may want to put through in my carreer. During the project I have had several meetings with the project coordinator where we discussed the role and how I could improve it. I think this was a great experience for me, especially because we were in such a large group.

Although my role as project manager took a fair amount of time I did manage to improve my testing abilities. I wrote multiple tests for different classes and methods, which in my eyes has given me a clear understanding of how tests should be used and what its use is.

Due to my project manager role I got a pretty clear overview of how projects work. I have had contact with the customers, context leaders, context coordinators and the team. I am now familiar with the Scrum framework, which taught me that there are many missteps to be made during a project.
Overall I think I can say I accomplished all of my learning goals.

\end{document}
