\documentclass[a4paper]{article}
\begin{document}

\title{Personal learning goals}
\author{Context project: Crisis management}

\maketitle

\section*{Learning goals} 

\subsection*{Calvin Wong Loi Sing}
\begin{itemize}
 	\item \LaTeX
	\item Teamwork within a group (`company')
	\item Scrum
	\item Architecture design and  implementation
	\item Unit Testing
\end{itemize}
The first goal I reached was improving my latex knowledge. Prior to working on the project I've dabbled with latex before, but never properly investigated how it worked. Usually my files were full of warnings, overfull or underfull boxes, and other issues. Luckily a member of my group had quite a bit of latex experience. From asking him certain questions and analyzing his latex documents I came to understand what I was doing wrong, and how these mistakes and issues can be mitigated.

My second goal, teamwork within a group, has also been reached. I really enjoyed the composition and organization of the team. The smaller groups within the team simulated a department within a company. I really liked this since it meant we'd have to learn how to communicate with the other groups (departments). Especially the creation of the Scenario Editor was a great learning experience, as we had to coordinate the work happening in two different groups. And because it didn't always go that smoothly I also gained valuable experience in detecting possible issues which could impede the teamwork. 

A project requirement was the use of Scrum and Trello for managing the process. Before the context project I've never had to use Scrum. While skeptical at first, in the end I couldn't have been happier with Scrum. The plans created using the Scrum method were usually completed at the end of the week, and I never felt as if I did too much or too little. Trello was also very handy to have, it makes keeping track of progress very easy. In fact, I enjoyed using Trello so much that I am currently using it in two separate projects as well.

The one goal I did not fully achieve was Architecture design and implementation. Our group (group 3) was mostly concerned with the scenario GUI, the human player GUI and in the end, the path planner. While we had to design and implement the Scenario GUI as it was made from scratch, I wasn't the same level of design and implementation I had in mind. I was mostly thinking about the refactoring that had to happen to BW4T, which group 1 did. But in the end I think I fit better in group 3 due to the fact that group 1 consisted mostly of TA's and I am sure that my second learning goal would have not been completed if I were in that group, since they had less contact time.

Finally, unit testing! It may seem weird to have it as a goal since one of the requirements for the context project is the successful completion of the course Software Quality \& Testing. However, after that course, I never got a chance to use my acquired knowledge in practice. It was fairly complicated for me when I started writing unit tests, especially since there were so many things to test, and our first project had a fairly large GUI which also had to be tested. But during the course of the project I slowly learned the best practices for testing.



\end{document}
