\section*{Usability Evaluation - Manual}

Dear test user, \\
\\
Welcome to our usability evaluation. This evaluation will consist of 2 parts: \\
\\
In the first part you will test our EnvironmentStore functionality, in the second part you will test our ScenarioEditor and run the just created Scenario in the HumanPlayer GUI. \\
\\
While making the assignments, please try to ‘think aloud’. That way we have a better understanding what’s going on in your head and why you make the choices you make. \\
\\

\subsection*{Part 1 (group 2)}
\textbf{Create your own map and save it}
\begin{enumerate}
\item Create a map with 7 rows and 8 columns.
\item Make sure the bots will have a place to start, to charge and to drop their blocks.
\item Create at least 1 blockade and 2 rooms.
\item Place some blocks into the rooms.
\item Create a color sequence which the bots will have to find.
\item Preview your map.
\item When finished, save your map.
\end{enumerate}

\textbf{Open your own map}
\begin{enumerate}
\item Open your own map.
\item Add another room.
\item Save it again.
\end{enumerate}

\textbf{Create a random map}
\begin{enumerate}
\item Open a new map.
\item Randomize the rooms.
\item Put random blocks into the rooms,\\
we want to maximize the possible number of blocks per room and no blue ones.
\item Create a random sequence.
\end{enumerate}

\newpage

\subsection*{Part 2 (Group 3)}
\textbf{Create your own scenario and save it}
\begin{enumerate}
\item Add two Human controlled bots.
\item Give them the colorblind handicap and give them a battery with capacity 50.
\item Add the mapfile you've just created to the Scenario.
\item Viisualize the paths and set collisions disabled.
\item Save the Scenario you've just created.
\end{enumerate}

\textbf{Open a saved scenario and export it}
\begin{enumerate}
\item Open the scenario you've saved.
\item Add a Human controlled bot.
\item Give the bot the gripper handicap.
\item Save the Scenario.
\item Use the MAS export to generate a mas2g project.
\end{enumerate}

\textbf{Run your scenario}
\begin{enumerate}
\item Find the first block of the sequence with bot1.
\item Tell bot2 were to find the block.
\item Let bot2 pick up the first block and bring it to the Dropzone.
\end{enumerate}

This is the end of the assignments, if you have any questions left, feel free to ask us.
\pagebreak