\section*{Personas}
\subsection*{Ad –-- Researcher}
Ad holds a masters degree in Computer Science and is a researcher in Multi-Agent systems and Artificial Intelligence. Together with his research group, he does research from the Technical University of Delft to explore the possibilities and restrictions in the field of agents and robots. His research focuses on the analysis, modeling, and development of agent technology that integrates different aspects of intelligence such as reasoning, decision-making, planning, learning and interaction but also integrates aspects such as emotional intelligence. This multi-agent technology has been applied, among others, in micro-simulation of domains such as traffic, logistics and supply chain management, serious gaming, negotiation, socio-cognitive robotics, and user modeling. 
As a researcher, Ad would like to use software that is complex in its possibilities but easy to use. He would like to run different simulations multiple times and track results easily.

\subsection*{Bob –-- PhD Student}
Bob is 27 years old en just finished with studying. He now owns a PhD in artificial intelligence programming. He lives alone in the city of Amsterdam and does not have a job yet. There is a competition coming up which he finds very interesting. In this competition you have to program an artificial intelligence for deep sea exploration. He really likes the idea of deep sea exploration and decides to take part in the competition. 
For the programming and testing of his AI Bob decides to use the programming language goal and the BW4T environment. He decides on this because he has used BW4T a lot during his studies and is well aware of the environment. Bob can use BW4T to simulate and if he has to even control his agents. He can also change the environment to scenarios he desires. He can change lots of things like: the speed to the bots, how far they can see and even the distance they can communicate with each other. He hopes to simulate deep sea conditions with these features.

\subsection*{Jasper --- Student}
Jasper is 18 years old, and is a first year student Computer Science at the TU Delft. He participates in the course Logic Based AI, and has to work with the GOAL programming language in the BW4T environment. The course is worth more points than it was last year (the previous course, Multi Agent Systems, was worth 3 points, while this new course is worth 5 points), so as an extra requirement to complete this part of the course, the bots all need to have a handicap, causing them to be unable to complete the problem individually but also causing them to be able to complete it as a team. To specify the required handicaps, Jasper uses the bot store built into the BW4T environment. 
He knows how to work with GOAL and the program itself, so that isn’t the problem. It needs to be clear for him how the handicaps are to be specified and what the handicaps do in terms of disabling the bots.

\subsection*{Paul –-- Professor}
Paul is a professor in Artificial Intelligence at the Technical University of Eindhoven. He teaches students in Computer Science who are in their second your of their bachelor program the course Engineering Multi-Agent Systems and together with his students he participates in different Multi-Agent and Robotics competitions because he thinks it is most important that the Technical University of Eindhoven spends much research in this field. This way he tries to exploit the possibilities of agents and artificial intelligence together with his students. 
To make Multi-Agent programming accessible to his students, Paul would like to use a system that is easy to use for the students but has limitless possibilities in ways of programming the agents. Furthermore, Paul would like to use the system to do research on Human-Computer Interaction and communication between different agents and would he like the simulations to be as realistic as possible concerning the different scenarios but does not value fancy graphics and animations. Paul is good with computers and assumes that his students are as well. 

\pagebreak