The roadmap starts at week 4, the start of the implementation. Below is our roadmap.

\begin{itemize}
  \item Week 4
  \begin{itemize}
    \item Launcher
      \item Core - Client - Server structure
    \item Scenario GUI design.
    \item Implement Scenario GUI design.
    \item Bot Store GUI design.
    \item Human player GUI design.
    \item Implement Bot Store GUI design.
    \item Beginning with Battery Functionality.
  \end{itemize}
  \textbf{v3.1}
  \item Week 5
  \begin{itemize}
    \item Documentation codeBase complete on package level.
      \item Wouter must know what the new architecture is.
      \item First integration with other teams.
      \item Make sure that the stakeholders get why we do what we do (eg. with repast).
    \item Implement Scenario GUI design with feedback.
    \item Finish Battery Functionality.
    \item Interface for handicaps.
    \item Implement handicaps.
    \item Beginning with design and implementation \gls{e-partner}.
  \end{itemize}
  \textbf{v3.2}
  \item Week 6
  \begin{itemize}
    \item Exception handling.
        \item Sonar issues.
        \item More specific documention codebase (core classes).
        \item Visualization package for Client en Server mergen.
    \item Implement \gls{e-partner} functionality.
    \item Completely finish \gls{e-partner}.
    \item Completely finish Bot Store.
    \item Environment Store GUI design.
    \item Complete Scenario GUI.
    \item Implement reading and loading config file.
    \item Implement batch runs.
    \item Integrate Scenario Editor GUI and Bot Store GUI.
  \end{itemize}
  \textbf{v3.3}
  \item Week 7
  \begin{itemize}
    \item Good graphical overview.
        \item Documentation codebase (complete class doc).
        \item  Make an overview of the system with CodeCity.
        \item  Analyse tool wich uses the logger. 
    \item Implement Environment Store design.
    \item Environment store: Manual map maker.
    \item Environment store: Random map maker.
    \item Completely finish batch runs.
    \item Implement Human player GUI design.
  \end{itemize}
  \textbf{v3.4}
  \item Week 8
  \begin{itemize}
    \item System works the same as before refactoring, functionalities are the same. 
        \item Fully integration tests.
        \item Test coverage of 50\% over the whole system.
    \item Completely finish Human player GUI.
    \item Completely finish Environment Store.
    \item Put the Environment Store GUI together with the other GUI's.
    \item Physical realism: \gls{pathfinding}/collision avoidance.
  \end{itemize}
  \textbf{v3.5}
  \item Week 9 
  \begin{itemize}
    \item Final bug fixes.
  \end{itemize}
  \textbf{v3.6}
  \item Week 10 
  \begin{itemize}
    \item Presentation final product.
  \end{itemize}
  \textbf{v4.0}
\end{itemize}

