\begin{itemize}
  \item Week 4
  \begin{itemize}
    \item User can click on buttons and fill in text fields in the Scenario Editor.
    \item User can use all the functionalities of the Bot Store GUI.
    \item User can save the data from the Bot Store UI. 
  \end{itemize}
  \textbf{v3.1}
  \item Week 5
  \begin{itemize}
    \item User can add, modify and delete bots and e-partners.
    \item User can use all the functionalities of the Bot Store GUI.
    \item User can save the data from the Bot Store UI. 
  \end{itemize}
  \textbf{v3.2}
  \item Week 6
  \begin{itemize}
    \item User can add, modify and delete bots and e-partners.
    \item User can use both the Scenario UI and the Bot Store UI together.
    \item User can make batch runs.
  \end{itemize}
  \textbf{v3.3}
  \item Week 7
  \begin{itemize}
    \item User can see the Environment Store GUI and already use some of the functionalities.
    \item User can see the Human Player GUI and already use some of the functionalities.
  \end{itemize}
  \textbf{v3.4}
  \item Week 8
  \begin{itemize}
    \item User can control a bot using the Human Player GUI.
    \item User can use all the functionalities of the Environment Store GUI.
    \item Bots can find alternative paths if they block each other.
    \item User can access all the different UI's. 
  \end{itemize}
  \textbf{v3.5}
  \item Week 9 
  \begin{itemize}
    \item User can run simulations combining all the UI's. 
    \item User can see the robots moving around in the environment. 
    \item System works the same as before refactoring.
  \end{itemize}
  \textbf{v3.6}
  \item Week 10 
  \begin{itemize}
    \item Presentation final product.
  \end{itemize}
  \textbf{v4.0}
\end{itemize}

